Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-15 paper.qmd
Updated Figure 3 title

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two projections from $7\\text{-}D$, for the two non-linear cluster data are shown. The sample obtained from the true model is shown, with the sample shown in grey and the true model in blue lines. In the C-shaped cluster, the data points are distributed randomly along the cluster, while the data is more concentrated more in one corner in the other non-linear cluster. Video of the langevitour animations are available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

@@

```{r}
#| label: fig-NLDR-two-curvy
#| echo: false
#| fig-cap: "Key steps for constructing the model on the UMAP layout ($k=2$): (a) data, (b) hexagon bins, (c) bin centroids, and (d) triangulated centroids. The two C-shaped clusters data is shown."
#| fig-width: 12
#| fig-height: 4
#| out-width: 100%

>>>>

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two projections from $7\\text{-}D$, for the two non-linear clusters data are shown. The sample obtained from the true model is shown, with the sample shown in grey and the true model in blue lines. In the C-shaped cluster, the data points are distributed randomly along the cluster, while the data is more concentrated more in one corner in the other non-linear cluster. Video of the langevitour animations are available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

@@

```{r}
#| label: fig-NLDR-two-curvy
#| echo: false
#| fig-cap: "Key steps for constructing the model on the tSNE layout ($k=2$): (a) data, (b) hexagon bins, (c) bin centroids, and (d) triangulated centroids. The two non-linear clusters data is shown."
#| fig-width: 12
#| fig-height: 4
#| out-width: 100%
